### 2012-06-06 trunk/paper-iswc-reification/commands.tex
first draft of the data model section
added example to the query section

\newcommand{\RDFplus}{RDF$^{\mathsf{\text{\tiny +\!meta}}}$}
\newcommand{\RDFplusTriple}{{\RDFplus} triple}

@@

@@

\newcommand{\symAllURIs}{\mathcal{U}} % the symbol for the set of all URIs
\newcommand{\symAllLiterals}{\mathcal{L}} % the symbol for the set of all literals
\newcommand{\symAllBNodes}{\mathcal{B}} % the symbol for the set of all blank nodes
\newcommand{\symAllVariables}{\mathcal{V}} % the symbol for the set of all query variables
	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it was required to define \symAllTRefs
\newcommand{\symAllTRefs}{\overline{\symAllTRefsInfinite}} % the symbol for the set of all triple references

\newcommand{\symTermsFct}{\mathrm{terms}} % the name used for \fctTerms
\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple/graph #1

\newcommand{\symTRefFct}{\mathrm{trefs}} % the name used for \fctTref
\newcommand{\fctTRef}[1]{\symTRefFct(#1)} % the set of all triple references in triple/graph #1

\newcommand{\symDerefFct}{\mathit{deref}} % the name used for \fctDeref
\newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1

@@

>>>>

\newcommand{\xxxPLUS}% % don't use that; it is required to define \RDFplus and \SPARQLplus
	%{$^{\mathsf{\text{\tiny +\!meta}}}$}
	{$^\star$}

\newcommand{\Reifi}{Reifi}
\newcommand{\ReifiPlus}{Reifi\xxxPLUS}
\newcommand{\RDFplus}{RDF\xxxPLUS}
\newcommand{\SPARQLplus}{SPARQL\xxxPLUS}

\newcommand{\RDFplusTriple}{{\RDFplus}\! triple}
\newcommand{\RDFplusGraph}{{\RDFplus}\! graph}
\newcommand{\TPplus}{tri\-ple\xxxPLUS pattern}

@@

\newcommand{\TRefPtt}{{\TRef} pattern}
\newcommand{\TRefPttLongVersion}{{\TRefLongVersion} pattern}

@@

\newcommand{\symDomFct}{\mathrm{dom}} % the name used for \fctDom
\newcommand{\fctDom}[1]{\symDomFct(#1)} % the domain of function/mapping #1

\newcommand{\symAllURIs}{\mathcal{U}} % the symbol for the set of all URIs
\newcommand{\symAllLiterals}{\mathcal{L}} % the symbol for the set of all literals
\newcommand{\symAllBNodes}{\mathcal{B}} % the symbol for the set of all blank nodes
\newcommand{\symAllVariables}{\mathcal{V}} % the symbol for the set of all query variables

	\newcommand{\symAllTriplesInfinite}{\mathcal{T}} % don't use that; it is required to define \symAllTriples
\newcommand{\symAllTriples}{\overline{\symAllTriplesInfinite}} % the symbol for the set of all triple references
	\newcommand{\symAllTPsInfinite}{\mathcal{TP}} % don't use that; it is required to define \symAllTPs
\newcommand{\symAllTPs}{\overline{\symAllTPsInfinite}} % the symbol for the set of all triple references

	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it is required to define \symAllTRefs
\newcommand{\symAllTRefs}{\overline{\symAllTRefsInfinite}} % the symbol for the set of all triple references
	\newcommand{\symAllTRefPttsInfinite}{\mathcal{RP}} % don't use that; it is required to define \symAllTRefPtts
\newcommand{\symAllTRefPtts}{\overline{\symAllTRefPttsInfinite}} % the symbol for the set of all triple reference patterns

\newcommand{\symTermsFct}{\mathrm{terms}} % the name used for \fctTerms
\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple #1

\newcommand{\symTermsPlusFct}{\symTermsFct^+} % the name used for \fctTermsPlus
\newcommand{\fctTermsPlus}[1]{\symTermsPlusFct\!(#1)} % the set of all terms in triple #1 and its embedded triples

\newcommand{\symTRefsFct}{\mathrm{trefs}} % the name used for \fctTrefs
\newcommand{\fctTRefs}[1]{\symTRefsFct(#1)} % the set of all triple references in triple/graph #1

% \newcommand{\symDerefFct}{\mathrm{deref}} % the name used for \fctDeref
% \newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1

% \newcommand{\symCloseFct}{\mathrm{cl}} % the name used for \fctClose
% \newcommand{\fctClose}[1]{\symCloseFct(#1)} % the tref-closure of #1

\newcommand{\symVarsFct}{\mathrm{vars}} % the name used for \fctVars
\newcommand{\fctVars}[1]{\symVarsFct(#1)} % the set of all variables in pattern #1

\newcommand{\symVarsPlusFct}{\mathrm{vars}^+} % the name used for \fctVarsPlus
\newcommand{\fctVarsPlus}[1]{\symVarsPlusFct\!(#1)} % the set of all variables in pattern #1 and its embedded patterns

\newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
\newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph
\newcommand{\fctDescentWP}[2]{\symDescentFct^{#1}\!(#2)} % the #1-based, RDF compatible expression of #2

@@

\newcommand{\OpAND}{\text{ \normalfont\scriptsize\textsf{AND} }}
\newcommand{\OpUNION}{\text{ \normalfont\scriptsize\textsf{UNION} }}
\newcommand{\OpOPT}{\text{ \normalfont\scriptsize\textsf{OPT} }}
\newcommand{\OpFILTER}{\text{ \normalfont\scriptsize\textsf{FILTER} }}
\newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
\newcommand{\OpSELECT}{\text{\normalfont\scriptsize\textsf{SELECT}}}
\newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
\newcommand{\fctEvalPlus}[2]{[\![#1]\!]^\star_{#2}} % the symbol for the evaluation of SPARQL* pattern #1 over an RDF* graph #2
\newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2

%% The following definitions of a symbol for left outer join work best in Springer format:
\def\ojoin{\setbox0=\hbox{$\Join$}\rule[.01ex]{.25em}{.45pt}\llap{\rule[1.05ex]{.25em}{.4pt}}}
\def\LJoin{\mathbin{\ojoin\mkern-7.5mu\Join}}

### 2012-06-06 trunk/paper-iswc-reification/querying.tex
added example to the query section

	Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$ where $\symAllVariables$ is a set of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively.
	%We assume a set $\symAllVariables$ of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively. Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$.
A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
%	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
%	For any {\TPplus} $tp \!=\! (s,p,o)$ we define $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.

@@

\subsection{({\RDFplus} Based) Semantics of {\SPARQLplus}}
	To define the semantics of {\SPARQLplus} we introduce
	%We define the semantics of {\SPARQLplus} based on
\emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note,
	%$\fctDom{\eta}$ denotes
	$\fctDom{\eta}$~denotes %% Layout Adjustment
the domain of a valuation $\eta$.

@@

@@

\todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}

\begin{proposition} \label{Proposition:JustificationForDataMinimality2}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
\end{proposition}

\todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}

@@

Let $P$ be a {\SPARQLplus} expression. We assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$. Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$. If $x \in \fctTRefs{P}$, then $w(x) := v(x)$; if $v \notin \fctTRefs{P}$, then $w(x) := x$.
%
Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w( rp )$ to denote
	the SPARQL expression $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
	%following SPARQL expression: \begin{align*}
	%	\Bigl( \Bigl( \,\, \Bigl( & \bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr) \Bigr) \OpAND \\
	%	& \bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr) \Bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr) \Bigr)
	%\end{align*}

The \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescent{P}^{w}$, is defined recursively as follows:
\begin{enumerate}
	\item If $P$ is a {\TPplus} $(s,p,o)$, and:
		\begin{enumerate}
			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $(s,p,o)$; or
			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
			\item else $\fctDescent{P}^w$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
		\end{enumerate}
		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w(s)$, $P_{s2}$ is $\fctDescent{s}^w$, $P_{o1}$ is $\mathrm{reif}^w(o)$, and $P_{o2}$ is $\fctDescent{o}^w$.
		\vspace{1ex}

	\item If $P$ is
			%$(tp \OpAS ?v)$ with $tp = (s,p,o)$,
			$\bigl( (s,p,o) \OpAS ?v \bigr)$,
		then $\fctDescent{P}^w$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.

% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.

		\vspace{1ex}
	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.

% 	\begin{tabular}{|c||c||c||c||c||c|} \hline
% 		$\boldsymbol{P}$ &
% 		$(P_1 \OpAND P_2)$ &
% 		$(P_1 \OpOPT P_2)$ &
% 		$(P_1 \OpUNION P_2)$ &
% 		$(P_1 \OpFILTER R)$ &
% 		$\OpSELECT_S(P_1)$
% 		\\ \hline
% 		$\boldsymbol{ \fctDescent{P}^w}$ &
% 		$(P_1' \OpAND P_2')$ &
% 		$(P_1' \OpOPT P_2')$ &
% 		$(P_1' \OpUNION P_2')$ &
% 		$(P_1' \OpFILTER R)$ &
% 		$\OpSELECT_S(P_1')$
% 		\\ \hline
% 	\end{tabular}
%
% 	\begin{center}
% 	\begin{tabular}{|c|c|} \hline
% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
% 		$(P_1 \OpAND P_2)$ & $(P_1' \OpAND P_2')$ \\ \hline
% 		$(P_1 \OpOPT P_2)$ & $(P_1' \OpOPT P_2')$ \\ \hline
% 	\end{tabular}
% 	\hspace{10mm}
% 	\begin{tabular}{|c|c|} \hline
% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
% 		$(P_1 \OpUNION P_2)$ & $(P_1' \OpUNION P_2')$ \\ \hline
% 		$(P_1 \OpFILTER R)$ & $(P_1' \OpFILTER R)$ \\ \hline
% 	\end{tabular}
% 	\end{center}
\end{enumerate}

\begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
	For any {\SPARQLplus} expression $P$ any RDF compatible expression of $P$ is an (ordinary) SPARQL expression.
\end{proposition}

>>>>

	Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$ where $\symAllVariables$ is a set of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively.
	%We assume a set $\symAllVariables$ of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively. Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$.
A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).

@@

\begin{example} \label{Example:SPARQLplusExpression}
		The following {\SPARQLplus} expression $P_\mathsf{ex}$ represents the query from Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before}:
		%We represent the query from Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before} using {\SPARQLplus} expression $P_\mathsf{ex}$:
	%
		%$\bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}), \mathTinyRDF{dct:source} , ?\mathit{src} \bigr)$.
		$\bigl( \, \bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \OpAS ?v \bigr) \OpAND (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \, \bigr)$.
% 	Let $P_\mathsf{ex}$ be the {\SPARQLplus} expression that represents the query in Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before}, that is, $P_\mathsf{ex}$ is
% 		%$\bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}), \mathTinyRDF{dct:source} , ?\mathit{src} \bigr)$.
% 		\begin{equation*}\Bigl( \bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \OpAS ?v \bigr) \OpAND (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \Bigr)\end{equation*}
	It holds $\fctVarsPlus{P_\mathsf{ex}} = \lbrace ?\mathit{who}, ?v, ?\mathit{src} \rbrace$ and $\fctTRefs{P_\mathsf{ex}} = \big\lbrace (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \big\rbrace$.
\end{example}

\subsection{({\RDFplus} Based) Semantics of {\SPARQLplus}}
To define the semantics of {\SPARQLplus} we introduce \emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note, $\fctDom{\eta}$ denotes the domain of a valuation $\eta$.

@@

\todo{adjust the following example once the previous examples are fixed}
\begin{example} \label{Example:SPARQLplusEvaluation}
	The evaluation of {\SPARQLplus} expression $P_\mathsf{ex}$ (cf.~Example~\ref{Example:SPARQLplusExpression}) over the {\RDFplusGraph} $G_\mathsf{ex}$ from Example~\ref{Example:ConvertingRDFplusToRDF} consists of a single valuation
		%$\eta_1$ (i.e.~$\fctEvalPlus{P_\mathsf{ex}}{G_\mathsf{ex}} = \lbrace \eta_1 \rbrace$)
		$\eta_1 \in \fctEvalPlus{P_\mathsf{ex}}{G_\mathsf{ex}}$
	such that $\fctDom{\eta} = \lbrace ?\mathit{who}, ?v, ?\mathit{src} \rbrace$ and $\eta(?\mathit{who})=\mathTinyRDF{:who}$, $\eta(?v)=(\mathTinyRDF{:who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase})$, and $\eta(?\mathit{src})=\mathTinyRDF{:src}$.
\end{example}

@@

% \todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}
% 
% \begin{proposition} \label{Proposition:JustificationForDataMinimality2}
% 	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
% \end{proposition}
% 
% \todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}

@@

Let $P$ be a {\SPARQLplus} expression.
	%We
	For converting $P$ to a SPARQL expression we
assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$. Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$. If $x \in \fctTRefs{P}$, then $w(x) := v(x)$; if $v \notin \fctTRefs{P}$, then $w(x) := x$.
%
Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w\!( rp )$ to denote
	the SPARQL expression $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
	%following SPARQL expression: \begin{align*}
	%	\Bigl( \Bigl( \,\, \Bigl( & \bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr) \Bigr) \OpAND \\
	%	& \bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr) \Bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr) \Bigr)
	%\end{align*}
%
Now, the \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescentWP{w}{P}$, is defined recursively: % as follows:
\begin{enumerate}
	\item If $P$ is a {\TPplus} $(s,p,o)$, and:
		\begin{enumerate}
			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescentWP{w}{P}$ is $(s,p,o)$; or
			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescentWP{w}{P}$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescentWP{w}{P}$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
			\item else $\fctDescentWP{w}{P}$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
		\end{enumerate}
		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w\!(s)$, $P_{s2}$ is $\fctDescentWP{w}{s}$, $P_{o1}$ is $\mathrm{reif}^w\!(o)$, and $P_{o2}$ is $\fctDescentWP{w}{o}$.
		\vspace{1ex}

	\item If $P$ is
			%$(tp \OpAS ?v)$ with $tp = (s,p,o)$,
			$\bigl( (s,p,o) \OpAS ?v \bigr)$,
		then $\fctDescentWP{w}{P}$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.

% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescentWP{w}{P}$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescentWP{w}{P_1}$ and $P_2'$ is $\fctDescentWP{w}{P_2}$.

		\vspace{1ex}
	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescentWP{w}{P}$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescentWP{w}{P_1}$ and $P_2'$ is $\fctDescentWP{w}{P_2}$.

% 	\begin{tabular}{|c||c||c||c||c||c|} \hline
% 		$\boldsymbol{P}$ &
% 		$(P_1 \OpAND P_2)$ &
% 		$(P_1 \OpOPT P_2)$ &
% 		$(P_1 \OpUNION P_2)$ &
% 		$(P_1 \OpFILTER R)$ &
% 		$\OpSELECT_S(P_1)$
% 		\\ \hline
% 		$\boldsymbol{ \fctDescentWP{w}{P}}$ &
% 		$(P_1' \OpAND P_2')$ &
% 		$(P_1' \OpOPT P_2')$ &
% 		$(P_1' \OpUNION P_2')$ &
% 		$(P_1' \OpFILTER R)$ &
% 		$\OpSELECT_S(P_1')$
% 		\\ \hline
% 	\end{tabular}
%
% 	\begin{center}
% 	\begin{tabular}{|c|c|} \hline
% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescentWP{w}{P}}$ \\ \hline \hline
% 		$(P_1 \OpAND P_2)$ & $(P_1' \OpAND P_2')$ \\ \hline
% 		$(P_1 \OpOPT P_2)$ & $(P_1' \OpOPT P_2')$ \\ \hline
% 	\end{tabular}
% 	\hspace{10mm}
% 	\begin{tabular}{|c|c|} \hline
% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescentWP{w}{P}}$ \\ \hline \hline
% 		$(P_1 \OpUNION P_2)$ & $(P_1' \OpUNION P_2')$ \\ \hline
% 		$(P_1 \OpFILTER R)$ & $(P_1' \OpFILTER R)$ \\ \hline
% 	\end{tabular}
% 	\end{center}
\end{enumerate}

\noindent
It is easy to see that our conversion function $\fctDescentWP{w}{P}$ replaces any \SPARQLplus-spe\-cif\-ic syntax element in $P$ by elements from the usual SPARQL syntax (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}). Thus:

\begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
	For any {\SPARQLplus} expression $P$ any ($w$-based) RDF compatible expression of $P$ is an ordinary SPARQL expression (for all possible $w$).
\end{proposition}

\todo{adjust the following example once the previous examples are fixed}
\begin{example} \label{Example:ConvertingSPARQLplusToSPARQL}
% 	Let $tp_\mathsf{ex}$ be the embedded {\TPplus} $(?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase})$ from Example~\ref{Example:SPARQLplusExpression} (i.e.~$tp_\mathsf{ex} \in \fctTRefs{P_\mathsf{ex}}$) and let $w(tp_\mathsf{ex})=?v$.
	For the {\SPARQLplus} expression $P_\mathsf{ex}$ from Example~\ref{Example:SPARQLplusExpression} holds that $\fctDescentWP{w}{P_\mathsf{ex}}$ is:
	\begin{align*}
		\bigl( \bigl( \bigl( \bigl( & (?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}) \OpAND (?v,\mathTinyRDF{rdf\!:\!subject},?\mathit{who}) \bigr) \OpAND \\
		& (?v,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{:bought}) \bigr) \OpAND (?v,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{:sybase}) \bigr) \bigr) \OpAND \\
		& (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \bigr)	
	\end{align*}
\end{example}
